What is an Ancestral Recombination Graph?

### 2022-02-13 paper.tex

	% Numbers of extant ancestors and links, from top to bottom
	\node[label=right:{Extant material}] at (7.5, 8.2) {};
	\node[label=right:{3 \; $3 L$}] at (7.5, 7.6) {};
	\node[label=right:{4 \; $4 L$}] at (7.5, 6.9) {};
	\node[label=right:{5 \; $5 L$}] at (7.5, 6.3) {};
	\node[label=right:{4 \; $4 L$}] at (7.5, 5.7) {};
	\node[label=right:{5 \; $5 L$}] at (7.5, 4.95) {};
	\node[label=right:{6 \; $6 L$}] at (7.5, 4.15) {};
	\node[label=right:{5 \; $5 L$}] at (7.5, 3.45) {};
	\node[label=right:{4 \; $4 L$}] at (7.5, 2.75) {};
	\node[label=right:{3 \; $3 L$}] at (7.5, 1.95) {};
	\node[label=right:{2 \; $2 L$}] at (7.5, 1.35) {};
	\node[label=right:{3 \; $3 L$}] at (7.5, 0.6) {};

	% Gray dashed lines to visually separate holding times
	\draw[color=gray, dashed] (7.5, 1.2) -- (11, 1.2); % D
	\draw[color=gray, dashed] (7.5, 1.5) -- (11, 1.5); % E and F
	\draw[color=gray, dashed] (7.5, 2.4) -- (11, 2.4); % G and H
	\draw[color=gray, dashed] (7.5, 3.1) -- (11, 3.1); % I and J
	\draw[color=gray, dashed] (7.5, 3.8) -- (11, 3.8);	% P and Q
	\draw[color=gray, dashed] (7.5, 4.5) -- (11, 4.5); % K
	\draw[color=gray, dashed] (7.5, 5.4) -- (11, 5.4); % L
	\draw[color=gray, dashed] (7.5, 6) -- (11, 6); % M and N
	\draw[color=gray, dashed] (7.5, 6.6) -- (11, 6.6);	% R
	\draw[color=gray, dashed] (7.5, 7.2) -- (11, 7.2); % O
\end{tikzpicture}
\end{tabular}
}
\caption{(A)
A realisation of the graph traversed by Hudson's algorithm started from a
sample of three continuous chromosomes of length $L$ at time $t = 0$, and
propagated until time $T$. The MRCA on the genetic interval $[x, z)$ is reached
at node L, while that on $[0, x)$ is reached at node O.
The non-ancestral segment $[x, y)$ above
node K contributes to the rate of effective recombinations because it
is trapped between ancestral segments. The two columns titled ``Extant
material" are the number of extant lineages and the total length of genetic
material on which an effective recombination can take place during each time
interval.
(B) A corresponding realisation of a big ARG, which augments Hudson's algorithm
by tracking nonancestral lineages. The result is a simpler state space and
dynamics, at the cost of extra nodes and edges, highlighted in red, which do
not affect the local tree at any site.}
\label{hudson_vs_bigARG}
\end{figure}

>>>>

	% Numbers of extant ancestors and links, from top to bottom
	\node[label=right:{CA \; RE}] at (7.5, 8.2) {};
	\node[label=right:{$\binom{3}{2}$ \; $3 L \rho$}] at (7.5, 7.6) {};
	\node[label=right:{$\binom{4}{2}$ \; $4 L \rho$}] at (7.5, 6.9) {};
	\node[label=right:{$\binom{5}{2}$ \; $5 L \rho$}] at (7.5, 6.3) {};
	\node[label=right:{$\binom{4}{2}$ \; $4 L \rho$}] at (7.5, 5.7) {};
	\node[label=right:{$\binom{5}{2}$ \; $5 L \rho$}] at (7.5, 4.95) {};
	\node[label=right:{$\binom{6}{2}$ \; $6 L \rho$}] at (7.5, 4.15) {};
	\node[label=right:{$\binom{5}{2}$ \; $5 L \rho$}] at (7.5, 3.45) {};
	\node[label=right:{$\binom{4}{2}$ \; $4 L \rho$}] at (7.5, 2.75) {};
	\node[label=right:{$\binom{3}{2}$ \; $3 L \rho$}] at (7.5, 1.95) {};
	\node[label=right:{$\binom{2}{2}$ \; $2 L \rho$}] at (7.5, 1.35) {};
	\node[label=right:{$\binom{3}{2}$ \; $3 L \rho$}] at (7.5, 0.6) {};

	% Gray dashed lines to visually separate holding times
	\draw[color=gray, dashed] (7.5, 1.2) -- (11, 1.2); 
	\draw[color=gray, dashed] (7.5, 1.5) -- (11, 1.5); 
	\draw[color=gray, dashed] (7.5, 2.4) -- (11, 2.4); 
	\draw[color=gray, dashed] (7.5, 3.1) -- (11, 3.1); 
	\draw[color=gray, dashed] (7.5, 3.8) -- (11, 3.8);
	\draw[color=gray, dashed] (7.5, 4.5) -- (11, 4.5); 
	\draw[color=gray, dashed] (7.5, 5.4) -- (11, 5.4);
	\draw[color=gray, dashed] (7.5, 6) -- (11, 6); 
	\draw[color=gray, dashed] (7.5, 6.6) -- (11, 6.6);
	\draw[color=gray, dashed] (7.5, 7.2) -- (11, 7.2); 
\end{tikzpicture}
\end{tabular}
}
\caption{(A)
A realisation of the graph traversed by Hudson's algorithm started from a
sample of three continuous chromosomes of length $L$ at time $t = 0$, and
propagated until time $T$. The MRCA on the genetic interval $[v, w)$ is reached
at event B, while that on $[0, v)$ is reached at event C.
The non-ancestral segment $[v, w)$ above
A contributes to the rate of effective recombinations because it
is trapped between ancestral segments. The two columns titled CA and RE
are the respective rates of mergers and recombinations when
the recombination rate is $\rho$.
(B) A corresponding realisation of a big ARG, which augments Hudson's algorithm
by tracking nonancestral lineages. The result is a simpler state space and
dynamics, at the cost of extra nodes and edges, highlighted in red, which do
not affect the local tree at any site.}
\label{hudson_vs_bigARG}
\end{figure}
